Assigning Scouts to Optimal Patrols

### 2016-05-25 draft1.tex

@@

%------------------------------------------------------------------------------
% End of journal.tex
%------------------------------------------------------------------------------
>>>>>>> 9771af696fbc57423120850744607162fcf171d5

>>>>

\begin{table}[h]
	\caption{}\label{eqtable}
	\renewcommand\arraystretch{1.5}
	\noindent\[
	\begin{array}{|c|c|}
	\hline
	\textbf{Patrol 1}&\textbf{Patrol 2}\\
	\hline
	\text{Brandon, Cameron, Colby,}&\text{Christian, Daniel, Jake,}\\
	\text{Darwin, Evan, Tommy}&\text{Jordan, Nathan, Patrick, Timmy}\\
	\hline
	\end{array}
	\]
\end{table}
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.60]{graph}
\end{figure}

\section*{Mathematical Model}
The problem of placing individuals into groups visually lends itself well to the notion of a mathematical graph. In mathematical vocabulary, a graph consists of a group of objects called vertices that get connected with an "edge" if they share some sort of relationship. The graph we will use to represent the data of our problem can be visualized with the image offered on page (5?), where vertices are represented by the circled names and edges are represented by lines between the circles. Since there is an inherent sense of relationships between individuals (how much a scout likes another scout), it is appropriate to consider the scouts as vertices in a graph with directed edges representing how much the “head” scout likes the “tail” scout. Our goal, using this language, is to find a partition of the vertices in the graph that satisfies some sort of objective function given size constraints of the partitions. In our problem at hand, we consider a complete graph with 13 vertices and edge weights being either 0, 1, or -1, corresponding to indifference, approval, or disapproval respectively of the “head” scout with respect to the “tail” scout. The Scoutmaster specifically wants two groups out of these 13, and with the size constraints for a patrol considered, our goal becomes finding 6 vertices to be in one partition and the other 7 being in another. The total number of partitions becomes 13 choose 6, which is equivalent to 1,716. This is certainly within the scope of considering total enumeration of the partitions as a reasonable solution to the problem, therefore we will proceed accordingly and implement the calculation using Python and its associated libraries to represent the data in a format that is convenient to work with.

%------------------------------------------------------------------------------
% End of journal.tex
%------------------------------------------------------------------------------
>>>>>>> 9771af696fbc57423120850744607162fcf171d5
=======
\documentclass{amsart}

@@

%------------------------------------------------------------------------------
% End of journal.tex
%------------------------------------------------------------------------------
